Artin Group Presentations of Reflection Groups

### 2014-07-18 Paper.tex
made some edits to jacob's part -aaron

\begin{lem}
Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
\begin{tikzcd}
i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
\end{tikzcd}
so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2') and $r(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (R3)(a) hold for C.
\end{lem}

@@

\begin{prop}\label{prop:ti_relations}
The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)^{\prime}$ and $(R3)^{\prime}$ associated to $\Gamma^{\prime}$.
\end{prop}

\begin{proof}[Proof of Theorem \ref{thm:main}]
Define a homomorphism $\varphi\colon A(\Gamma^{\prime}) \rightarrow A(\Gamma)$ by sending each generator $s_i\in A(\Gamma^{\prime})$ to $t_i\in A(\Gamma)$.  This gives a well-defined homomorphism by Proposition \ref{prop:ti_relations}.  By Lemma \ref{lem:op_homomorphism}, the homormorphism $\Delta\colon A(\Gamma) \rightarrow A(\Gamma^{op})$ that sends $s_i\in A(\Gamma)$ to $s_i^{-1}$ in $A(\Gamma^{op})$ is well-defined.  Define a homomorphism 
$$\psi = \Delta\circ\varphi\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$

Note that here we use the facts that $\left(\Gamma^{op}\right)^{op} = \Gamma$ and $\left(\Gamma^{op}\right)^{\prime} = \left(\Gamma^{\prime}\right)^{op}$.  Suppose that there is an arrow $i\rightarrow k$ in $\Gamma$.  Then there will be an arrow $k\rightarrow i$ in $\Gamma^{op}$ and hence an arrow $i\rightarrow k$ in $\left(\Gamma^{op}\right)^{\prime}$, so we have that

$$\psi\circ\varphi(s_i) = \Delta(\varphi(\Delta(\varphi(s_i)))) = \Delta(\varphi(\Delta(s_ks_is_k^{-1}))) = \Delta(\varphi(s_k^{-1}s_i^{-1}s_k)) = \Delta(s_i^{-1}) = s_i$$

Similarly if there is an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\Gamma$ then there will be an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\left(\Gamma^{op}\right)^{\prime}$, respectively.  In each of these cases we have that

@@

\begin{proof}[Proof of Proposition \ref{prop:ti_relations}]
First we check the $(R2)'$ relation for $t_i$ and $t_j$ in the case when $i=k$ or $j=k$.  Without loss of generality suppose that $i=k$.  Note that $m_{ij}^\prime = m_{ij}$.  The only nontrivial case is when there is an arrow $j\rightarrow k =i$.  Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.  Suppose $m_{ij} = 3$.  Then $s_js_is_j = s_is_js_i$, so $s_is_j = s_js_is_js_i^{-1}$, and we have

@@

$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{1-}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$

@@

$$t_it_jt_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_it_jt_i$$

Next we check the $(R2)'$ relation for $t_i$ and $t_j$ in the case when at most one of $i$ and $j$ is connected to $k$.  The only nontrivial case is when there is an arrow $i\rightarrow k$ or $j\rightarrow k$.  Without loss of generality, suppose there is an arrow $i\rightarrow k$.  Since $j$ is not connected to $k$, we know that $s_js_k = s_ks_j$.  Suppose $m_{ij} = 2$.  Then $s_is_j = s_js_i$, so we have that

$$t_it_j = s_ks_is_k^{-1}s_j = s_js_ks_is_k^{-1} = t_jt_i$$

>>>>

\begin{lem}
Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:

\begin{equation*}
\begin{tikzcd}
i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
\end{tikzcd}
\end{equation*}
so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2') and $r(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (R3)(a) hold for C.
\end{lem}

@@

\begin{prop}\label{prop:ti_relations}
The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)^{\prime}$ and $(R3)^{\prime}$ associated to $\Gamma^{\prime}$.
\end{prop}
\todo{This propositions seems to be worded confusingly. I see this is what they say in Barot and Marsh, but I still find it confusing. Maybe it's clearer to say that if we take $p_i$ to be the generators of $\Gamma',$ and they satisfy a relation $r(p_1,\ldots, p_{|\Gamma|}) = e,$ if and only if $t_i$ satisfy the same relation $r(t_1,\ldots, t_{|\Gamma|}) = e.$}
\todo{Maybe it would make more sense to break this up into 2 lemmas, like Barot and Marsh do}

\begin{proof}[Proof of Theorem \ref{thm:main}]
Define a homomorphism $\varphi\colon A(\Gamma^{\prime}) \rightarrow A(\Gamma)$ by sending each generator $s_i\in A(\Gamma^{\prime})$ to $t_i\in A(\Gamma)$. \todo{Weren't the $t_i$ defined in terms of the $s_i$ for $A(\Gamma)$? It seems like there are two different $s_i,$ one for $\Gamma$ and one for $\Gamma'$ and this is confusing me.}  This gives a well-defined homomorphism by Proposition \ref{prop:ti_relations}.  By Lemma \ref{lem:op_homomorphism}, the homormorphism $\Delta\colon A(\Gamma) \rightarrow A(\Gamma^{op})$ that sends $s_i\in A(\Gamma)$ to $s_i^{-1}$ in $A(\Gamma^{op})$ is well-defined.  Define a homomorphism 
$$\psi = \Delta\circ\varphi\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$
\todo{It seems like there is an abuse of notation here. You have defined $\phi:A(\Gamma') \rightarrow A(\Gamma),$ but it looks like it is mapping $A(\Gamma^{op} \rightarrow A((\Gamma^{op})')$ here. Please make clearer what this map $\phi$ is.}
Note that here we use the facts that $\left(\Gamma^{op}\right)^{op} = \Gamma$ and $\left(\Gamma^{op}\right)^{\prime} = \left(\Gamma^{\prime}\right)^{op}$.  Suppose that there is an arrow $i\rightarrow k$ in $\Gamma$.  Then there will be an arrow $k\rightarrow i$ in $\Gamma^{op}$ and hence an arrow $i\rightarrow k$ in $\left(\Gamma^{op}\right)^{\prime}$, so we have that

$$\psi\circ\varphi(s_i) = \Delta(\varphi(\Delta(\varphi(s_i)))) = \Delta(\varphi(\Delta(s_ks_is_k^{-1}))) = \Delta(\varphi(s_k^{-1}s_i^{-1}s_k)) = \Delta(s_i^{-1}) = s_i$$
\todo{I think you have the right idea, but I don't understand how you always have elements in $A(\Gamma)$ and never elements in $A(\Gamma').$ I think the problem lies in the definition of $\phi.$}
Similarly if there is an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\Gamma$ then there will be an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\left(\Gamma^{op}\right)^{\prime}$, respectively.  In each of these cases we have that

@@

\begin{proof}[Proof of Proposition \ref{prop:ti_relations}]
First we check the $(R2)'$ relation for $t_i$ and $t_j$ in the case when $i=k$ or $j=k$.  Without loss of generality suppose that $i=k$.  Note that $m_{ij}^\prime = m_{ij}$. The only nontrivial case is when there is an arrow $j\rightarrow k =i$. \todo{Isn't there also the case of an arrow from k to j? Obviously it's symmetric, but isn't it worth saying?}  Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.  Suppose $m_{ij} = 3$.  Then $s_js_is_j = s_is_js_i$, so $s_is_j = s_js_is_js_i^{-1}$, and we have

@@

$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$

\todo{An extra step inserting and removing inverses here would be helpful.}

@@

$$t_it_jt_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_it_jt_i$$
\todo{An extra step inserting and removing inverses here would be helpful, as above}

\todo{Instead of saying If mij = 3, try \vskip.1in
\noindent
{\sf The case $m_{ij} = 3$}}

Next we check the $(R2)'$ relation for $t_i$ and $t_j$ in the case when at most one of $i$ and $j$ is connected to $k$.  The only nontrivial case is when there is an arrow $i\rightarrow k$ or $j\rightarrow k$.  Without loss of generality, suppose there is an arrow $i\rightarrow k$.  Since $j$ is not connected to $k$, we know that $s_js_k = s_ks_j$.  Suppose $m_{ij} = 2$. \todo{It seems like the previous two sentences should be switched? Again try using cases to break it up more clearly for the reader, as I mentioned in a previous todo.} Then $s_is_j = s_js_i$, so we have that

$$t_it_j = s_ks_is_k^{-1}s_j = s_js_ks_is_k^{-1} = t_jt_i$$
\todo{It looks like you're also using here that $s_j$ commutes with $s_k^{-1}.$ I agree it's obvious, but maybe it's worth spelling out}
